\documentclass[10pt]{article}

\begin{document}
\section*{Development Ideas}
\begin{enumerate}
    \item Android App - Type to shut off
    \item Android App - Crypt It!
    \begin{itemize}
        \item Users can encrypt phrases, sentences
        \item Select from multiple encryption techniques
        \item Can automatically decrypt based on proper keyword
        \item Multithreading, reflection needed?
    \end{itemize}
    \item Web App or Android App - Typing Game
    \begin{itemize}
        \item 2 people - attack / defend
        \item SQL database to store coins and username and password
        \item coins use to customzie user - hats, weapon skins, etc.
        \item faster person wins
        \item tug of war maybe?
        \item or maybe a zombie attack and defend
        \begin{itemize}
            \item longer word = longer life
            \item user gets to pick whether to attack or defend
            \item tab key = switch state (attack / defend)
            \item attack = choose letter word by pressing number first - then type word
            \item defend = simply type the word
            \item select from predefined words of certain length such that user cant just randomly press letters
            \item \textbf{first iteration: single player against zombies?}
        \end{itemize}
    \end{itemize}
    \item Phone App - Security Multiplayer Game
    \begin{itemize}
        \item Players attempt to guess each other's security password
        \item See how vulnerable passwords are
        \item Spend on upgrades -- use complex symbols, increase character count, etc.
    \end{itemize}
    \item Machine Learning - Detect Cancer?
    \begin{itemize}
        \item Parse through data, see if there's a correlation between cancer and data?
    \end{itemize}
    \item Hardware - Robot Cleaner
    \begin{itemize}
        \item Cameras installed
        \item Uses computer vision to detect trash
        \item Learn what trash installed
        \item Use camera underneath to pick it up
    \end{itemize}
    \item Brainwave API - Video Game
    \item Artificial Intelligence
\end{enumerate}
\end{document}